Named Entity Recognition as Structured Prediction

### 2012-11-09 doc/report/paper.tex
++++methods

\subsection{Methods employed for NER}
For \emph{NER}, there exist both rule-based and statisical approaches. 
Rule-based methods make use of the underlying rules governing languages to extract named entities. 
However, this approach is high maintenance, quite time-consuming and requires extensive work of computational linguists \cite{nadeau2007survey}
and although the results are often high in precision, lacks considerably in recall.

In regard to statistical approaches, supervised-learning is the most common method applied in \emph{NER}. Although, there are unsupervised approaches, 
their performance is not as high as for SL applications yet.

Prominent algorithms in NER include maximum entropy models,

@@

\subsection{CoNLL Data and Baseline Performance}
The training and test data for Spanish \& Dutch was taken from the \emph{CoNLL Shared Task 2002} \cite{tksintro} and 
the \emph{CoNLL Shared Task 2003} \cite{TjongKimSang:2003:ICS:1119176.1119195} provided the one for English \& German.
The ConNLL shared tasks are organised challenges, where the organisers propose a task and provide the participants with the
training and test data. 
In 2002 and 2003, the task was Named Entity Recognition. 
In both years, the baseline rate for the individual languages was produced by a system, that had a unique class in the training data. 
In case that a phrase was part of more than one entity, the system would choose the longest one \cite{TjongKimSang:2003:ICS:1119176.1119195}. 
Table \ref{table:Base} shows the baseline for the four different languages.  
The data is annotated with part-of-speech tags and named-entity tags, as well as Bio-tags that indicate the position in the Named Entity. 
Our approach is based on the system that won the challenge for English and German in 2003.

@@

\subsection*{Evaluation}
For the evaluation of the system we used \emph{Precision} and \emph{Recall} as shown in \ref{Precision} and \ref{Recall} respectively.
The general formula for the \emph{F-Score} is shown in \ref{Fscore}. Since we rate both \emph{Precision} and \emph{Recall} evenly, we 
use the harmonic mean as shown in \ref{F1}.

>>>>

\subsection{Methods employed for NER}
For \emph{NER}, there exist two general approaches: one is rule-based and the other statistical. 
Rule-based methods make use of the underlying rules governing a language to extract the named entities. 
This approach, however, is rather high maintenance and requires extensive work by experts such as computational linguists \cite{nadeau2007survey}.
The results are often quite high in precision, but lack considerably in recall. % rules are partly language-dependent

For statistical approaches, supervised-learning is the most commonly method applied in \emph{NER}. 
There are unsupervised methods, but they cannot compete with SL applications yet.
Prominent algorithms in NER include maximum entropy models,

@@

\subsection{CoNLL Data and Baseline Performance}
The training and test data for Spanish \& Dutch was taken from the \emph{CoNLL Shared Task 2002} \cite{tksintro} and 
the \emph{CoNLL Shared Task 2003} \cite{TjongKimSang:2003:ICS:1119176.1119195} provided the one for English \& German.
The ConNLL shared tasks are organised challenges, where the organisers propose a task and provide the participants with the
training and test data. 
In 2002 and 2003, the task was Named Entity Recognition. 
In both years, the baseline rate for the individual languages was produced by a system, that had a unique class in the training data. 
In case that a phrase was part of more than one entity, the system would choose the longest one \cite{TjongKimSang:2003:ICS:1119176.1119195}. 
Table \ref{table:Base} shows the baseline for the four different languages.  
The data is annotated with part-of-speech tags and named-entity tags, as well as Bio-tags that indicate the position in the Named Entity. %put in ``tokenized, chunked''
Our approach is based on the system of \cite{strlearn} that won the challenge for English and German in 2003.

@@

\subsection*{Evaluation}
For the evaluation of the system we used \emph{Precision} and \emph{Recall} as shown in \ref{Precision} and \ref{Recall} respectively.
Precision is the percentage of Named Entities found by the system that are correct. Recall represents the the percentage of 
named entites present in the corpus that were found by the system. 
A named entity is only deemed correct if it is an exact match for the corresponding data file.
The general formula for the \emph{F-Score} is shown in \ref{Fscore}. Since we rate both \emph{Precision} and \emph{Recall} evenly, we 
use the harmonic mean as shown in \ref{F1}.
